\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{fancyhdr}

% Page layout
\geometry{left=1in, right=1in, top=0.8in, bottom=0.8in}

% Remove default page numbers
\pagestyle{empty}

% Customize section headers (all black now)
\titleformat{\section}{\large\bfseries\color{black}}{}{0em}{}
\titlespacing*{\section}{0pt}{10pt}{5pt}

% Customize itemize
\setlist[itemize]{leftmargin=*,itemsep=2pt,parsep=0pt}

% Custom commands for contact info
\newcommand{\contactinfo}[3]{\faPhone~#1 \quad \faEnvelope~\href{mailto:#2}{#2} \quad \faMapMarker*~#3}

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{Karthikeyan Sugumaran}} \\
    \vspace{5pt}
    \contactinfo{+91 9008889204}{yeskarthi@gmail.com}{} \\
    \faLinkedin\ \href{https://www.linkedin.com/in/yeskarthi/}{linkedin.com/in/yeskarthi} \\
    \vspace{10pt}
\end{center}

% Horizontal line
\noindent\rule{\textwidth}{0.4pt}
\vspace{10pt}

% Professional Summary
\section*{Professional Summary}
\begin{flushleft}
    Wireless LAN technology leader with over 24 years of experience at Qualcomm, Atheros, Broadcom, Athenasemi, and Telesilikon. Expertise in 802.11 standards, chip definition, silicon bring-up, software design, device drivers, firmware, and customer feature delivery. Specialized in WLAN product design for access points, scan radios, and stations across enterprise, retail, and carrier segments. 

    \mbox{} \\

    Recognized for strong leadership, people management, and program execution skills. Experienced in guiding multi-disciplinary teams through the complete product lifecycle --- from concept and definition to high-volume deployment. Adept at aligning product strategy with business goals while mentoring and developing engineering talent.

    \mbox{} \\

    Recent focus on integrating AI and machine learning into Wi-Fi solutions to enhance network performance, predictive diagnostics, and anomaly detection. Successfully led product definition, engineering, and cross-functional teams across hardware, software, and verification groups, delivering high-volume WLAN solutions globally.
\end{flushleft}

\mbox{} \\

% Core Skills
\section*{Core Skills}
\begin{itemize}
    \item \textbf{Wireless}: 802.11 (a--bn), Bluetooth, Coexistence
    \item \textbf{WLAN Product Design}: Access points, scan radios, stations (Enterprise, Retail, Carrier)
    \item \textbf{People Management}: Building and mentoring high-performing teams, career development, fostering innovation
    \item \textbf{Program Management}: End-to-end execution, milestone ownership, risk management, customer deliverables
    \item \textbf{Product Leadership}: Definition, roadmap execution, cross-functional alignment
    \item \textbf{Cross-Functional Collaboration}: HW/SW integration, global teams, multi-geo delivery
    \item \textbf{Embedded Systems}: Device drivers, firmware, system integration
    \item \textbf{Programming Languages}: C, Python, Shell
    \item \textbf{Software Development Methodologies}: Agile, Waterfall, Iterative, etc.
    \item \textbf{Emerging Technologies}: Wi-Fi + AI/ML solutions for network optimization and analytics
\end{itemize}

\mbox{} \\

% Domain Expertise
\section*{Domain Expertise}
\begin{flushleft}
Wireless communication technologies, computer networking, operating systems, system architecture and design, product definition and development, system performance optimization, and KPI analysis and tuning.
\end{flushleft}

\mbox{} \\

% Work Experience Summary
\section*{Work Experience Summary}
\begin{flushleft}
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{@{} l l X @{}}
\textbf{Company} & \textbf{Period} & \textbf{Role} \\
\hline
Qualcomm India Private Limited & 2011--Present & Sr. Staff Engineer \\
Atheros LLC India Private Limited & 2008--2011 & Lead Engineer \\
Broadcom India Private Limited & 2005--2008 & Sr. Staff Engineer \\
AthenaSemi & 2002--2005 & Sr. Firmware Engineer \\
TeleSilkin & 2000--2002 & Firmware Engineer \\
A.D.E & 1999--2001 & Contract Engineer \\
\end{tabularx}
\end{flushleft}

\mbox{} \\

% Experience
\section*{Experience}
\textbf{Senior Staff Engineer \& Product Engineer} \hfill 2001--Present \\
\textit{Qualcomm | Atheros | Broadcom | Athenasemi | Telesilikon} \\
\begin{itemize}
    \item Defined product features and guided silicon-to-software development across multiple Wi-Fi generations, enabling successful product launches.
    \item Built and managed high-performing engineering teams, fostering innovation and accountability, and drove programs from inception to successful completion.
    \item Mentored junior engineers and established structured development processes, resulting in career growth and improved retention.
    \item Coordinated cross-functional hardware, software, and verification teams across geographies, ensuring milestone alignment and on-time delivery.
    \item Led program planning, execution tracking, and risk management for global WLAN product releases.
    \item Designed WLAN solutions for access points, scan radios, and stations, addressing enterprise, retail, and carrier needs.
    \item Developed AI/ML-enhanced Wi-Fi solutions, improving network performance, interference management, and predictive diagnostics.
\end{itemize}

\mbox{} \\

% Achievements
\section*{Achievements}
\begin{itemize}
    \item Contributed to WLAN evolution from 802.11a through 802.11bn.
    \item Shipped multiple high-volume WLAN chipsets for global markets.
    \item Successfully managed distributed cross-geo technical teams for product releases, balancing engineering execution with business priorities.
    \item Drove customer-facing feature delivery and resolved complex field issues.
    \item Applied AI/ML to Wi-Fi networks for traffic optimization and anomaly detection.
    \item Recognized for leadership in mentoring, team building, and driving organizational capability growth.
\end{itemize}

\mbox{} \\

% Patents
\section*{Patents}
\begin{itemize}
    \item \textsc{US20180027518A1} -- Proximity sensing using spectral analysis.
    \item \textbf{(Filed)} -- Access Point (AP) spectral scan using neural networks (NN).
\end{itemize}

\mbox{} \\

% Education
\section*{Education}
\textbf{B.E. Electronics and Communication Engineering} \hfill 1994--1998 \\
\textit{Bangalore University}

\pagestyle{fancy}
\fancyfoot[C]{\today} % Center footer with current date

\end{document}
